% Adapted from https://github.com/Nadorrano/cv-friggeri-x
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% cv-friggeri-x 1.0 (01/01/2016)
% XeLaTeX Template
%
% Based on:
% Friggeri Resume/CV
% Version 1.2 (3/5/15)
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% Modified by:
% Nadorrano
% https://github.com/Nadorrano/cv-friggeri-x
%
% License:
% MIT (https://opensource.org/licenses/MIT)
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography,
% if used, needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,nocolors]{cv-friggeri-ben}
% Add `a4paper` to set a4 paper size
% Add `nocolors` to remove colors from the document
% Add `lightheader` to change the dark background of the header to white

% \usepackage{marvosym} % needed to print glyphs for email, cell phone etc.
\usepackage{fancyhdr}  % For footer
\renewcommand{\headrulewidth}{0pt}  % Remove horizontal header rule
\addbibresource{publications.bib} % Specify the bibliography
\urlstyle{same}  % URL style in bib

\begin{document}

\header{BEN~}{MORCOS}{full(er) stack developer} % Your name and current job title/field

%%%%%%%%%%%%%%%%%%%
% SIDEBAR SECTION %
%%%%%%%%%%%%%%%%%%%

\begin{aside} % In the aside, each new line forces a line break
    \section{CONTACT}
    \hfill Waterloo
    \hfill Ontario, Canada
    \vspace{0.5\baselineskip} \hfill +1.519.729.3223
    \hfill \href{mailto:morcos.ben@gmail.com}{morcos.ben@gmail.com}
    % \flogo \hfill \href{http://facebook.com/johnsmith}{fb://jsmith}
    % \tlogo \hfill \href{http://twitter.com/johnsmith}{@jsmith}
    % \llogo \hfill \href{http://linkedin.com/johnsmith}{in://johnsmith}
    % \vklogo \hfill \href{http://vk.com/johnsmith}{vk://johnsmith}
    % ~
    \vspace{0.5\baselineskip} \hfill%
    \href{https://github.com/bmorcos}{github.com/bmorcos}
    %
    \section{LANGUAGES}
    English, French
    %
    \section{PROGRAMMING}
    Python, C, C++
    OpenCL, CUDA
    VHDL, Verilog, HLS
    JavaScript, TypeScript
    \LaTeX, shell, Tcl
    VBA
    %
    \section{TOOLS}
    GitHub, GitLab
    TravisCI, Codecov
    pytest, GTest
    TensorFlow, TFMOT
    NNI, Hyperopt
    MongoDB, GraphQL
    Conda, Docker
    Vivado, Quartus
    AutoCAD, SolidWorks
    MATLAB, Simulink
    kdenlive, inkscape
    %
    \section{OPEN IP}
    \href{https://github.com/abr/zynq-axi-dna}{zynq-axi-dna}
    \href{https://github.com/abr/c5soc-ocl-id}{c5soc-ocl-id}
    \href{https://github.com/bmorcos/pre-commit-hooks-cpp}{pre-commit-hooks-cpp}
    \href{https://github.com/bmorcos/discord-downloader}{discord-downloader}
    \par\vspace{0.5\baselineskip}\textbf{CONTRIBUTOR}
    \href{https://github.com/nengo/nengo}{nengo}
    \href{https://github.com/nengo/nengo-fpga}{nengo-fpga}
    %
    \section{HOBBIES}
    Hiking \& Canoeing
    Climbing
    Woodworking
    Music
    Cooking
    Various sports
    Philosophy
\end{aside}


%%%%%%%%%%%%%%%%
% QUICK SKILLS %
%%%%%%%%%%%%%%%%

\vspace{-1em}\hspace{-4.33cm}
\textbf{\large{%
\hfill SOFTWARE \hfill {\small\textbullet}%
\hfill EMBEDDED \hfill {\small\textbullet}%
\hfill AI/ML \hfill {\small\textbullet}%
\hfill SYSTEM~DESIGN \hfill {\small\textbullet}%
\hfill HARDWARE \hfill%
}}%

\vspace{-1ex}\hspace{-4.33cm}\hrulefill


%%%%%%%%%%%%
% ABOUT ME %
%%%%%%%%%%%%
\vspace{-2pt}
\section{ABOUT ME}

My academic and work experience has given me development skills at many levels
of abstraction. I have worked on everything from gate-level hardware to
embedded software to frontend clients, and everything in between. This breadth
of knowledge led me to the label \emph{full(er) stack developer} and I
appreciate the perspective this affords me when designing systems and working
across teams. I'm always looking to hone my skills and continue to learn new
things. However, I am currently most interested in the middle of the full(er)
stack from embedded to core application to backend.



%%%%%%%%%%%%%%%%%%%%%%%%%%%
% WORK EXPERIENCE SECTION %
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{WORK EXPERIENCE}

\begin{entrylist}

\entry
    {2016--Now}
    {Applied Brain Research}
    {Waterloo, ON}
    {\emph{Neuromorphic Software-Hardware Co-Developer}
    \begin{itemize}
        \item Lead efforts to explore, optimize, and implement neural
            applications on various standard, embedded, and neuromorphic
            hardware platforms.
        \item Establish a common high-level interface, via GUIs and APIs, for
            deploying neural networks across various hardware platforms.
        \item Provide low-level libraries, interfaces, and protocols for
            modular embedded neural deployments.
        \item Bring to market edge AI web platform.
        \item Devise novel AI/ML solutions and benchmarking for dynamical tasks.
        \item Leverage model pruning and quantization techniques.
        \item Collaborate with leading scientists pushing the boundaries of
            computational neuroscience applications including autonomy, vision,
            speech, and more.
        \item Single handedly develop run-time flexible FPGA implementation to
            efficiently run dynamic neural networks with a user-friendly Python
            interface.
        \item Evaluate possible ASIC designs for sparse, event-driven dynamic
            neural networks.
        \item Maintain clean code repositories with automated devops pipelines.
        \item Manage and mentor co-op and Mitacs students.
        \item Assist with yearly \emph{Nengo Summer School} --- a two week
            in-depth workshop for international scholars to learn and use Nengo.
    \end{itemize}}

\entry
    {2014--2015}
    {Teledyne DALSA {\normalfont (co-op \times2)}}
    {Waterloo, ON}
    {\emph{Mechanical Designer}, \emph{Sustaining Engineer}
    \begin{itemize}
        \item Designed and validated custom fixtures for testing and production.
        \item Optimized and debugged software and hardware of vision sensors.
    \end{itemize}}

\entry
    {2014}
    {Toyota Motor Manufacturing Canada {\normalfont (co-op)}}
    {Cambridge, ON}
    {\emph{Quality Control Engineer for Lexus Hybrid group}
    \begin{itemize}
        \item Performed root cause analysis and coordinated trial solutions.
    \end{itemize}}

\entry
    {2013}
    {Intellijoint Surgical {\normalfont \emph{formerly Avenir Medical} (co-op)}}
    {Waterloo, ON}
    {\emph{Medical Device Designer}
    \begin{itemize}
        \item Implemented and evaluated optical feature extraction algorithms.
    \end{itemize}}

\entry
    {2012--2013}
    {IKO Industries {\normalfont (co-op \times2)}}
    {Madoc, ON}
    {\emph{Mechanical Engineer}, \emph{Electrical \& Systems Engineer}
    \begin{itemize}
        \item Improved throughput by 13\% with analysis and recommendation.
        \item Optimized sensors, PLC, and HMI.
    \end{itemize}
    }
\end{entrylist}


\pagebreak
%%%%%%%%%%%%%%%%%%%%%
% EDUCATION SECTION %
%%%%%%%%%%%%%%%%%%%%%

\section{EDUCATION}

\begin{entrylist}

\entry
    {2017--2019}
    {MASc {\normalfont --- Computer Hardware Engineering}}
    {\\The University of Waterloo}
    {Developed a neuromorphic hardware accelerator on FPGAs with a focus on
    run-time flexibility and accessibility. The hardware is conveniently
    connected to Python via the Nengo development framework and is run-time
    configurable to support a wide range of neural networks with a static
    hardware design.}

\entry
    {2011--2016}
    {BASc {\normalfont --- Mechatronics Engineering, with distinction}}
    {\\The University of Waterloo}
    {The Mechatronics program covers a broad base of mechanical, electrical,
    computer, and system design engineering while my elective courses leaned
    towards philosophy, machine intelligence, and neuroscience. My capstone
    design project was a small-scale portable hydro-electric generator built
    from scratch.}

\end{entrylist}


%%%%%%%%%%%%%%%%%%%%%%%%
% PUBLICATIONS SECTION %
%%%%%%%%%%%%%%%%%%%%%%%%

\section{PUBLICATIONS}

% \printbibsection{inproceedings}{~}
% \printbibsection{thesis}{~}
\printallbibsections


%%%%%%%%%%%%%%%%
% VOLUNTEERING %
%%%%%%%%%%%%%%%%

\section{VOLUNTEER WORK}

\begin{entrylist}

\entry
    {2017--Now}
    {The Foodbank of Waterloo Region}
    {Kitchener, ON}
    {Work at the distribution warehouse to sort food and keep track of
    local inventory. This is a fun, low mental effort, and social position that
    benefits the community --- everybody wins!}

\entry
    {2017}
    {Teaching Assistant}
    {Heterogeneous Architecture Summer School}
    {Assisted with a one week workshop teaching students about computation using
    heterogeneous hardware platforms (FPGA, GPU, CPU).}

\entry
    {2014--2015}
    {Federation Orientation Committee}
    {The University of Waterloo}
    {One of four volunteers responsible for planning Engineering Orientation
    Week 2015 for $\approx$2000 incoming students:
    \begin{itemize}
        \item Interviewed, hired, and managed a team of $\approx$400 volunteers.
        \item Obtained sponsorship and created a formal budget for the year.
        \item Worked alongside numerous other entities within the University.
        \item Kept well documented records for continuous improvement.
    \end{itemize}}

% \entry
%     {2011--2015}
%     {Campus Response Team}
%     {The University of Waterloo}
%     {Providing emergency first-aid for on-campus events.\\
%     \emph{Operations Coordinator} --- 2014
%     \begin{itemize}
%         \item Manage and improve day-to-day and event operations.
%     \end{itemize}
%     \emph{Director of Training} --- 2012--2013
%     \begin{itemize}
%         \item Organize weekly training and termly first-aid competition.
%     \end{itemize}}

\end{entrylist}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CERTIFICATIONS & AWARDS %
%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{CERTIFICATIONS \& AWARDS}
% \vspace{-2pt}

% \begin{entrylist}

% % \entry
% %     {2009--2020}
% %     {Advanced Medical First Responder}
% %     {\\Canadian Ski Patrol System \& St. John Ambulance}
% %     {I used to volunteer as a ski patrol at Mt. Tremblant, QC and then I was
% %     a member of the Campus Response Team during my undergrad. I no longer
% %     actively provide first-aid but I still maintain my certification!}

% \entry
%     {2013}
%     {NSERC Industrial Undergraduate Student Research Award}
%     {Intellijoint Surgical}
%     {\vspace{-11pt}}

% \entry
%     {2012}
%     {Nominated as Co-op Student of the Year}
%     {The University of Waterloo}
%     {\vspace{-11pt}}

% \entry
%     {2011}
%     {President's Scholarship}
%     {The University of Waterloo}
%     {\vspace{-11pt}}

% \end{entrylist}


%%%%%%%%%%
% FOOTER %
%%%%%%%%%%

\thispagestyle{fancy}  % Show footer
\fancyfootoffset[L]{4.6cm}  % Compensate for sidebar
\fancyhf{}  % Clear header and footer tempaltes
\lfoot{\small\addfontfeature{Color=lightgray}Last updated 2021-11-18}

\end{document}
